Realizability-Preserving Two-Moment DG Method for Fermionic Transport \tnoteref{ldrd-support}

### 2018-01-29 Documents/M1/realizableFermionicM1/sections/realizability.tex
Modified the plot of convex set R.

\begin{lemma}
  The set $\cR$, defined in Eq.~\eqref{eq:realizableSet}, is convex.  
\end{lemma}
\begin{proof}
  A convex set $Q$ is a set has the following property: 
  \begin{equation*}
  \theta a + (1-\theta)b \in Q,~\text{for}~\forall a, b \in Q~\text{and}~0\leq\,\theta\,\leq1. 
  \end{equation*} 
  Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ to be two arbitrary elements of $\cR$.
  If $\cR$ is convex, we will have $\vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} = \theta \vect{\cM}_{a} + (1-\theta)\vect{\cM}_{b}$ in $\cR$ with $0\leq\theta\leq1$.
  The first component of $\vect{\cM}_{ab}$ is
  \begin{equation*}
  \cJ_{ab} = \theta \cJ_{a} + (1-\theta)\cJ_{b}.
  \end{equation*}
  Since $\theta$, $\cJ_{a}$, $1-\theta$ and $\cJ_{b}$ are all nonnegative, $\cJ_{ab}$ is also nonnegative.
  Meanwhile, since $\cJ_{a}\leq1$ and $\cJ_{b}\leq1$, $\cJ_{ab}\leq1$.
  That's $\cJ_{ab} \in [0,1]$.
  The second component is
  \begin{equation*}
  \vect{\cH}_{ab} 
  = \theta \vect{\cH}_{a} + (1-\theta)\vect{\cH}_{b}.
  \end{equation*}
  Using Jensen's inequality,
  \begin{equation*}
  \gamma(\vect{\cM_{ab}}) \leq \theta\gamma(\vect{\cM_{a}}) + (1-\theta)\gamma(\vect{\cM_{b}}) \leq 0.
  \end{equation*}
\end{proof}

The Fig.~\ref{fig:RealizableSetFermionic} illustrates how the convex realizable set $\cR$ looks like in $|\vect{\cH}| - \cJ$ coordinates.  
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{figures/RealizableSetFermionic}
\caption[Numerical plot of the convex realizable set $\cR$.]{
A numerical plot of the convex realizable set $\cR$.
The blue line are the boundary given by $\gamma(\vect{\cM}) = 0$. 
The red line are the boundary given by $|\vect{\cH}| = \cJ$.
Every black dot represents a sample whose distribution function $\mathfrak{f}(\mu)$ is an arbitrary Fermi-Dirac function and its angular moments were given by integrals using Trapezoid rule.
Total 1000,000 $\mathfrak{f}(\mu)$ were sampled for making this plot.}
\label{fig:RealizableSetFermionic}
\end{figure}

>>>>

\begin{lemma}
  The set $\cR$, defined in Eq.~\eqref{eq:realizableSet}, is convex.  
\end{lemma}
\begin{proof}
  A convex set $Q$ is a set has the following property: 
  \begin{equation*}
  \theta a + (1-\theta)b \in Q,~\text{for}~\forall a, b \in Q~\text{and}~0\leq\,\theta\,\leq1. 
  \end{equation*} 
  Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ to be two arbitrary elements of $\cR$.
  If $\cR$ is convex, we will have $\vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} = \theta \vect{\cM}_{a} + (1-\theta)\vect{\cM}_{b}$ in $\cR$ with $0\leq\theta\leq1$.
  The first component of $\vect{\cM}_{ab}$ is
  \begin{equation*}
  \cJ_{ab} = \theta \cJ_{a} + (1-\theta)\cJ_{b}.
  \end{equation*}
  Since $\theta$, $\cJ_{a}$, $1-\theta$ and $\cJ_{b}$ are all nonnegative, $\cJ_{ab}$ is also nonnegative.
  Meanwhile, since $\cJ_{a}\leq1$ and $\cJ_{b}\leq1$, $\cJ_{ab}\leq1$.
  That's $\cJ_{ab} \in [0,1]$.
  Since the second derivative of $\gamma(\vect{\cM})$ is $-2$ which is always negative, $\gamma(\vect{\cM})$ is a concave function.
  Using Jensen's inequality, we have
  \begin{equation*}
  \gamma(\vect{\cM_{ab}}) \geq \theta\gamma(\vect{\cM_{a}}) + (1-\theta)\gamma(\vect{\cM_{b}}) \ge0.
  \end{equation*}
\end{proof}

The Fig.~\ref{fig:RealizableSetFermionic} illustrates how the convex realizable set $\cR$ looks like in $|\vect{\cH}| - \cJ$ coordinates.
Total 1000,000 distribution functions having form $\mathfrak{f}(\mu;a,b) = \dfrac{1}{e^{a+b\mu}+1}$ were evaluated.
The parameters, $a$ and $b$, were chosen from $[-100,100]$ independently.
The variable $\mu$ ranges from $-1$ to $1$ with $d\mu=\f{1}{128}$.
And the integrals in angular moment expressions are calculated using Trapezoid rule.
\begin{figure}
\centering
\includegraphics[width=1.0\linewidth]{figures/RealizableSetFermionic}
\caption[Numerical plot of the convex realizable set $\cR$.]{
A numerical plot of the convex realizable set $\cR$.
The black line are the boundary given by $\gamma(\vect{\cM}) = 0$. 
The red line are the boundary given by $|\vect{\cH}| = \cJ$.
Every light-blue dot represents a sample whose distribution function $\mathfrak{f}(\mu)$ is an arbitrary Fermi-Dirac function and its angular moments were given by integrals using Trapezoid rule.
Total 1000,000 $\mathfrak{f}(\mu)$ were sampled for making this plot.}
\label{fig:RealizableSetFermionic}
\end{figure}
